Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-10-30 ms.tex
compared the illum changes to the 487/489 slope ratio.

\begin{figure*}
\gridline{
\fig{illum_slope_and_intercept.pdf}{0.49\textwidth}{Illumination Gradient Change over Time}
}
\caption{The illumination gradient changes as a function of time for the AZlab06 baseline test detector 487..}\label{fig:illumGradientChangeOverTime}
\end{figure*}

>>>>

\begin{figure*}
\gridline{
\fig{illum_slope_and_intercept.pdf}{0.49\textwidth}{Illumination Gradient Change over Time}
}
\caption{The illumination gradient changes as a function of time for the AZlab06 baseline test detector 487.
The illumination gradient explains some but not all of the correlated noise when dividing detector 487 by 489.}\label{fig:illumGradientChangeOverTime}
\end{figure*}
